\cleardoublepage
\pagestyle{plain}
\section*{Acknowledgements}

My thanks goes to Prof. Dr Sonja Grün for providing an open and creative environment permitting the development of this thesis.\newline

My deepest gratitude goes to Dr. Michael Denker for sharing his excitement and infinite motivation to pursue the rather infrastructural topics covered in this thesis.\newline

Also I would like to thank Dr. Lyuba Zehl for frontiering these topics and laying the foundations for me to build on.\newline

In general I would thank all the lab members of the INM-6 who became friends during my extended time at the INM-6. Thanks for all the fun, boring, tasty, silly, secret, creative and cycling time you shared with me. This specially includes the openness to provide refuge for me being stuck in Jülich or Düren.\newline

I also would like to thank all collaborative partners of the INM-6 I had the chance to work with. This especially includes the ComCo group in Marseille, the G-Node in Munich and the \software{Neo} collaboration.\newline

My thanks also goes to my current flatmates and friends with whom I also shared very cheerful, tasty, sportive and playful times, although unfortunately I was busy way too often.\newline

I would also like to thank Sam, Kila and their companions, who countless times risked their lifes for my distraction.
\newline

Last but not least I would also like to thank my family for their persistent nosiness as well as their support in mental and physical ways. Vielen Dank für den Apfelbrei, Oma!\newline

\vfill
\textcolor{gray}{\rule{0.3\textwidth}{0.4pt}\\
\smaller
Financially the work presented in this thesis was partly supported by Helmholtz Portfolio “Supercomputing and Modeling for the Human Brain” (SMHB), EU Grants 604102, 720270 and 785907 (Human Brain Project, HBP), Priority Program SPP 1665 of the DFG (GR1753/4-2 and DE 2175/2-1), Collaborative Research Agreement RIKEN-CNRS, ANR GRASP, CNRS (PEPS, Neuro\_IC2010), DAAD, LIA Vision for Action, HDS-LEE: Helmholtz School for Data Science in Life, Earth and Energy (Jülich, Aachen, Köln) and BMBF grants 01GQ1302 and 01GQ1509.}
